Lawvere-Tierney Sheafification in Homotopy Type Theory

### 2016-04-08 paper/paper_lipics.tex
minor changes

The development uses the new universe polymorphism feature of
Coq~\cite{sozeau2014universe}. However, it still lacks some features, and
in the formalization, we had to use the \texttt{type-in-type} option, to handle
the universe issues we faced. If not totally satisfactory, this option
is a convenient way to write the Coq code, the following
universes issues being checked on paper, like in the library
Unimath\footnote{\url{https://github.com/UniMath}, {Vladimir
    Voevodsky, Benedikt Ahrens, Daniel Grayson and others}}.

@@

%
This restriction in our formalization may be solved by
generalizing the management of universe polymorphism for recursive definition
%
and by the use of general ``resizing axioms'' which are still under
discussion in the community.
%
We note that for this solution to work, we need to have a more general 
definition of modalities than the one in~\cite{hottlib}, which ask the
reflector $\modal$ to map a universe $\Type^i$ to
itself. Here, we relax this constraint by allowing the reflector to
map a universe $\Type^i$ to a
possibly higher universe $\Type^j$. 
We have checked that the library~\cite{hottlib} still works with this
generalized definition after minor modifications (see
\url{https://github.com/KevinQuirin/HoTT/tree/extended_modalities/} for the
formalization).

@@

In this paper, we have defined a way to extend homotopy type theory
with new principles, leveraging Lawvere-Tierney sheafification to
homotopy type theory. 
%
Using sheafification, it is possible to add new logical principles to
homotopy type theory, such as the law of excluded middle, and this
without axiom.
%
Beyond this result, our work is part of a more general line of work
which aim to illustrate that homotopy type theory is a very promising
theory for formalizing mathematics inside a proof assistant.

>>>>

The development uses the new universe polymorphism feature of
Coq~\cite{sozeau2014universe}. However, it still lacks some features, and
in the formalization, we had to use the \texttt{type-in-type} option, to handle
the universe issues we faced. If not entirely satisfactory, this option
is a convenient way to check the whole construction in Coq, but for
universes.
%
The following universe issues have being checked on paper, like in the
Unimath
library.\footnote{\url{https://github.com/UniMath}, {Vladimir Voevodsky, Benedikt Ahrens, Daniel Grayson and others}}

@@

%
So universe issues in our formalization may be solved by
generalizing the management of universe polymorphism for recursive definition
%
and also by using of general ``resizing axioms'' which are still under
discussion in the community.
%
We note that for this solution to work, we need to have a more general 
definition of modalities than the one in~\cite{hottlib}, which ask the
reflector $\modal$ to map a universe $\Type^i$ to
itself. Here, we relax this constraint by allowing the reflector to
map a universe $\Type^i$ to a
possibly higher universe $\Type^j$. 
We have checked that the library~\cite{hottlib} still works with this
generalized definition after minor modifications (see
\url{https://github.com/KevinQuirin/HoTT/tree/extended_modalities/} for the
formalization).

@@

In this paper, we have defined a way to extend homotopy type theory
with new principles, leveraging Lawvere-Tierney sheafification to
homotopy type theory. 
%
Using sheafification, it is possible to add new logical principles to
homotopy type theory, such as the law of excluded middle, and this
without axiom.
%
Beyond this result, our work is part of a more general line of work
which aims to illustrate that homotopy type theory is a very promising
theory for formalizing mathematics inside a proof assistant.
